\documentclass[12pt]{article}
%Gummi|065|=)
\usepackage{amsmath, amsfonts, amssymb}
\usepackage[margin=0.5in]{geometry}
\usepackage{xcolor}
%\usepackage{graphicx}
%\usepackage{graphicx}
\newcommand{\off}[1]{}
\DeclareMathSizes{20}{30}{21}{18}

\newcommand{\myhrule}{}

\newcommand{\dash}{
\begin{tikzpicture}[scale=0.35]
\foreach \x in {1,...,55}{
	\draw (\x,-0.25)--(\x+0.5,0.25)--(\x+1,-0.25);
}
\end{tikzpicture}
}

\newcommand{ \sk }{
\begin{tikzpicture}
\draw (0,0)--(18,0);
\end{tikzpicture} \\
}

\usepackage{tikz}

\title{\textbf{ Problem:  AMC 12A (2016)}}
\author{John D Mangual}
\date{}
\begin{document}

\fontfamily{qag}\selectfont \fontsize{25}{32}\selectfont

\maketitle

\noindent  \textbf{Problem} What is the value of $\displaystyle \frac{11!-10!}{9!} $ ? \\ \\
(A) 99 \; (B) 100 \; (C) 110 \; (D) 121 \; (E) 132

\begin{tikzpicture}
\draw (0,0)--(18,0);
\end{tikzpicture} \\
Better get multiplying!  And we don't have a calculator on this test!  What is this?
$$1 \times 2 \times 3 \times 4 \times 5
\times 6 \times 7 \times 8 \times 9 \times 10 \times 11 $$
I know that $2^{10} = 1024$ or is it $512$?  Not important right now:
$$ 1 \times 2 \times 3 \times 4 = 24 $$
and then multiply by $5 \times 6 = 30$ so that makes 
$$ 1 \times 2 \times 3 \times 4 \times 5
\times 6  = 24 \times 30 = 720$$
Just five moroe numbers left.
$$ 7 \times 8 = 56 \;\;\;\;\;\;\;\; 9\times 10 \times 11 = 990 $$
so what is $56 \times 990$ this is not getting us very far.

\newpage

\noindent $11!$ is some very large number\footnote{hopefully you know what the factorial symbol means}.
$$ 11! = 11 \times 10! $$
Then maybe we can subtract against the other $10!$
$$ \frac{11! - 10!}{9!}
= \frac{10! \times (11 - 1) }{9!} 
= 9 \times 10 = 90$$
That would be choice \\
and that was none of the choices\,...
$$ \frac{11 \times 10! - 10!}{9!} = (11 - 1) \times \frac{10 \times 9!}{9!}= 100$$
The answer is choice \textbf{(B)}.  

\sk
\textbf{Alterantive} If we took remainders upon division modulo 10.  Forget it.
$$  \frac{11! - 10!}{9!}$$
$9!$ is a very complicated thing.  Since $2 < 9$ and $5 < 9$ we have that $10$ divides $9!$ -- this is not relevant.
$$ \frac{11 \times 10 \times 9! - 10 \times 9!}{9!} = 11 \times 10 - 10 = 100$$ 

\newpage

\noindent The peculiar thing about this problem is that we rarely need the last decimal place of a large number!  If I said:
$$ 10! \approx 10^{10}$$
that might be convincing enough.  But that is not right since: 
\begin{itemize}
\item $  1 < 10$
\item $ 2 < 10$
\item $ 3 < 10$
\item $\dots$
\item $ 9 < 10$
\item $10 = 10$
\end{itemize}
Then if we multiply all these inequalities together
$$ 1 \times 2 \times 3 \times \dots \times 9 \times 10 < 10^{10}$$
So how bad is our estimate?  That must wait for another time... 

\newpage

\noindent The other place this number might appear:
$$ 6 = 3! = \# \big| \{ ABC, ACB, BAC, BCA, CAB, CBA \} \big|$$
The factorials $n!$ count the number or re-orderings of a word. \\ \\ So how do we ascribe meaning to this? \\
$$  \frac{ \text{rearrange 11 letters}
- \text{rearrange 10 letters}}{ \text{rearrange 9 letters}}$$
Let's rearrange the letters $\{ a,b,c,d,e,f,g,h,i,j,k\}$.
$$  \text{any letter is not }a \Big| \text{ any letter } \Big| \text{everything else} $$
and this is another reason why $\boxed{10! < 10^{10}!}$ is because we are not allowing repeats: \\
\begin{itemize}
\item \textbf{NO} AABBCCDDEEF
\item \textbf{YES} ABCDEFGHIKJ
\end{itemize}

\newpage

\noindent \textbf{Scratchwork} if I could find the last digit mod 10 I'd be done:
$$ \frac{11! - 10!}{9!}  \equiv x \text{ mod } 10 $$
Then multiply both sides by $9!$ some very large perculiar number we don't fully understand.
$$ 11! - 10!  \equiv 9! x \text{ mod } 10 \times 9!$$
Rather disappointly this does not yield anything new.  This merely yields one of the solutions we've presented before.
\end{document}