\documentclass[12pt]{article}
%Gummi|065|=)
\usepackage{amsmath, amsfonts, amssymb}
\usepackage[margin=0.5in]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}

% zeta functions of cubic fields

%\usepackage{pifont}
\usepackage{amsmath}

\newcommand{\off}[1]{}
\DeclareMathSizes{20}{30}{20}{18}

\newcommand{\two }{\sqrt[3]{2}}
\newcommand{\four}{\sqrt[3]{4}}
\newcommand{\red}{\begin{tikz}[scale=0.25]
\draw[fill=red, color=red] (0,0)--(1,0)--(1,1)--(0,1)--cycle;\end{tikz}}
\newcommand{\blue}{\begin{tikz}[scale=0.25]
\draw[fill=blue, color=blue] (0,0)--(1,0)--(1,1)--(0,1)--cycle;\end{tikz}}
\newcommand{\green}{\begin{tikz}[scale=0.25]
\draw[fill=green, color=green] (0,0)--(1,0)--(1,1)--(0,1)--cycle;\end{tikz}}

\newcommand{\sq}[3]{\draw[#3] (#1,#2)--(#1+1,#2)--(#1+1,#2+1)--(#1,#2+1)--cycle;}

\usepackage{tikz}

\newcommand{\susy}{{\bf Q}}
\newcommand{\RV}{{\text{R}_\text{V}}}

\title{Scratchwork: Motives}
\date{}
\begin{document}

%\fontfamily{qag}\selectfont \fontsize{12.5}{15}\selectfont

\sffamily

\maketitle

\noindent I have been learing from these wonderful notes of Brian Conrad (UConn) but I'm coming to different conclusions about his own material.  He doesn't like the conclusions I've been coming to.  I'm gingerly telling him that . \\ \\
\textbf{Prop} The Galois Group of $x^3 - 3x - 1$ is $A_3 = \{ (1),(123),(132) \} $. \\ \\
The even permutations of three elements - there are only three of them.  The roots are: $r, r^2 - r - 2, -r^2 + 2$. \\ \\
In order to do polynomial manipulations, I used \texttt{sympy}, a Python language polynomial manipulation tool.  Certainly Galois didn't have that available to him.   You merely add an import statement like: \\ \\
\texttt{from sympy import *} \\ \\
and then you have to identify the correct functions.  I need to write some polynomial congruences\dots the \textit{remainders} of in polynomial division. Our number field is:
$$ K = \mathbb{Q}[x]/(x^3 - 3x - 1)$$ 
and we have $[K:\mathbb{Q}] = 3$ and the Galois group has $|A_3|= 3$ elements.  Therefore the map $r \mapsto r^2 - r - 2$ can be represented as a $3 \times 3$ matrix:
$$\begin{array}{ccccc}
1 & \mapsto & 1 \\
x & \mapsto & x^2 - x - 2 \\
x^2 & \mapsto & - x^2 + 2
\end{array}  :
\left[ 
\begin{array}{rrr} 1 &  0 & 0 \\
-2 & -1 & 1 \\ 2 & -1 & 0\end{array}\right]
\left[ \begin{array}{l} 1 \\ x \\ x^2 \end{array}\right]$$
and the other element of the Galois group $r \mapsto - r^2 + 2$ can be represented as another $3 \times 3$ matrix.
$$\begin{array}{ccccc}
1 & \mapsto & 1 \\
x & \mapsto & - x^2 + 2 \\
x^2 & \mapsto  & x^2 - x - 2 
\end{array}  :
\left[ 
\begin{array}{rrr} 1 &  0 & 0 \\
2 & 0 & -1 \\ 4 & 1 & -1\end{array}\right]
\left[ \begin{array}{l} 1 \\ x \\ x^2 \end{array}\right]$$
what remains to check this is is a representation of $A_3$:
$$ \left[ 
\begin{array}{rrr} 1 &  0 & 0 \\
-2 & -1 & 1 \\ 2 & -1 & 0\end{array}\right]^3 =  \left[ 
\begin{array}{rrr} 1 &  0 & 0 \\
2 & 0 & -1 \\ 4 & 1 & -1\end{array}\right]^3 = 
\left[ 
\begin{array}{rrr} 1 &  0 & 0 \\
0 & 1 & 0  \\ 0 & 0 & 1 \end{array}\right]$$ 
This is not to be taken for granted that these matrices behave.\footnote{and always lots of interesting mistake} \\\\
The goal is to get these computations to look visually nice enough to fit on a placard.  I have told you every cubic (only Galois group $A_3$) leads this kind of triangle in 3 dimensional space, using only integers.  So maybe there is a way of feeling Galois theory with Euclidean geomtry?  He did not like that.

\vfill

\begin{thebibliography}{}

\item Brian Conrad \textbf{Galois Groups of Cubics and Quartics} \\ \texttt{http://www.math.uconn.edu/\~{}kconrad/blurbs/galoistheory/cubicquartic.pdf}
 
\end{thebibliography} 

\noindent Next time $S_3$ cubic extensions, now $[K:\mathbb{Q}]= 6$. \\ \\
\textbf{1/20} The discriminant of a polynomial is easy to define if we look only at the roots.  This comes from a time when people tried to solve equations by hand:
$$  (x- a)(x - b)(x-c)
= x^3 - (a+b+c)x^2 + (ab+bc+ca)x - abc$$
and we need a condition for these three roots to be distinct, we obtain:
$$ (a-b)(b-c)(c-a) = \left|
\begin{array}{ccc} 
1 & a & a^2 \\
1 & b & b^2 \\
1 & c & c^2 \end{array} \right| $$
Another useful invariant is called the ``resultant" which involves sytems of equations.  In the 19th century, being a mathematician meant being very good at manipulating these kinds of algebraic expressions.  In the 20th century we have gone the opposite extreme seeking more conceptual approaches.  In the 21st centery everything is becoming quite ``catgorial", so far. \\ \\
I am arguing that doing explicit computations, by hand without the aid of a computer, has never gone away.  That computers can do a lot of heavy lifing for us but mostly we are still on our own. \\ \\
I had wondered for a bit about symmetric polynomials and if they tell us information.  Galois' original letters from when he was a teenager are available online (in French) without a trip to the library - he uses symmetric polynomials in a rather creative way and I always wondered how he stated his result. Conrad uses a theorem  that comes out of nowhere. \\ \\
There's also this inequality:
$$  \frac{a+b+c}{3} \geq \sqrt[3]{abc} $$
Our polynomial was: $x^3 - 3x - 1 $ so that $a+b+c = 0$ and $abc = 1$.  We learn that:
$$ \left[ 0= \frac{0}{3} \right] \geq \left[ \sqrt[3]{1} = 1 \right] $$
This is good.  We have shown that $\mathbf{0 \geq 1}$. Did we know that the roots $a> 0$ or $b > 0$ or $c > 0$, or that $a,b,c \in \mathbb{R}$ ? \\  \\
We need to check where Conrad found his theorems. And we need a source of ``totally real" number fields.  Even if the Galois group is $\mathbb{Z}/3\mathbb{Z}$ such as $K = \sqrt[3]{3}$, there will be other problems.  We get a variant of Pell equation:
$$ N(a + b\sqrt[3]{3} + c\sqrt[3]{9})
= a^3 + 3b^3 + 9 c^3 - 9abc = 1 $$
While it's possible that ``norms" are negative, in this field we also caution this equation has infinitely many integer solutions.
\newpage

\noindent Here's a result that Avila and Delecroix report that enable us to produce totally real cubics.  Start with three matrices:

$$ 
A = \left[
\begin{array}{ccc} 
1 & 0 & 0 \\
1 & 1 & 0 \\
1 & 0 & 1
\end{array} \right] \;
B = \left[
\begin{array}{ccc} 
1 & 1 & 0 \\
1 & 0 & 0 \\
0 & 0 & 1
\end{array} \right] \;
C = \left[
\begin{array}{ccc} 
1 & 0 & 1 \\
0 & 1 & 1 \\
0 & 0 & 1
\end{array} \right] $$
These matrices correspond to basic operations you can do on sets of three numbers:
$$ (a,b,c) \mapsto (a,a+b,a+c) \text{ or }  (a+b,b,a+c) \text{ or }  (a+c,b+c,c)$$
This has to do with the ``fully subtractive" continued fraction algorithm.  We've written additions.  Let's try the inverse operation:
$$ 
\left[
\begin{array}{ccc} 
1 & 0 & 0 \\
1 & 1 & 0 \\
1 & 0 & 1
\end{array} \right]^{-1}
= \left[
\begin{array}{rcc} 
1 & 0 & 0 \\
-1 & 1 & 0 \\
-1 & 0 & 1
\end{array} \right] $$
Any time you multiply these three matrices, and include each of $A$, $B$, $C$, you get a number that is \textbf{Pisot}.\footnote{Why did I say ``totally real"?  Pisot numbers can have imaginary complex conjugates.}  These numbers are elements of $\mathbb{C}$ and we could study the diophantine properties of these numbers (basically... different types of ``rounding").  These matrices guarantee us a single real root $\lambda$ with $|\lambda | < 1$.  \\ \\
Let's just multily them and enjoy the result:
$$ 
ABC = \left[
\begin{array}{ccc} 
1 & 0 & 0 \\
1 & 1 & 0 \\
1 & 0 & 1
\end{array} \right] \left[
\begin{array}{ccc} 
1 & 1 & 0 \\
1 & 0 & 0 \\
0 & 0 & 1
\end{array} \right] \;\left[
\begin{array}{ccc} 
1 & 0 & 1 \\
0 & 1 & 1 \\
0 & 0 & 1
\end{array} \right]
= 
\left[
\begin{array}{ccc} 
1 & 1 & 2 \\
2 & 1 & 3 \\
1 & 1 & 3
\end{array} \right] $$
and we could have characteristic polynomilal of cubics:
\begin{eqnarray*}
\left|
\begin{array}{lll} 
1 -x& 1 & 2 \\
2 & 1-x & 3 \\
1 & 1 & 3-x
\end{array} \right| 
&=&  x^3 -(1+1+3)x^2 +\left( \left|
\begin{array}{cc}
1 & 3 \\ 1 & 3 \end{array} \right|
+ 
\left|
\begin{array}{cc}
1 & 2 \\ 1 & 3 \end{array} \right| 
+
\left|
\begin{array}{cc}
1 & 1 \\ 2 & 3 \end{array} \right|\right) x -
\left|
\begin{array}{ccc} 
1 & 1 & 2 \\
2 & 1 & 3 \\
1 & 1 & 3
\end{array} \right| \\ \\
&=& x^3 - 5 x^2 + 2x + 1
\end{eqnarray*}
This will suffice for our search for Galois theory examples. \\ \\  With cubic fields, there are only a few outcomes $S_3$ or $A_3 \simeq \mathbb{Z}/3\mathbb{Z} = C_3$ or $\mathbb{Z}/3\mathbb{Z} \times \mathbb{Z}/2\mathbb{Z} \simeq \mathbb{Z}/6\mathbb{Z}$. \\\\ If we can do the examples more carefully we have an endless supply of Galois groups to calculate. \\ \\
\noindent \textbf{Ex} The period $(1, \sqrt[3]{2}, \sqrt[3]{4})$ of the Brun continued fraction algorithm is worked out in [Brun54].  It is 19.  This can be checked using decimals or algebraically storing the algebraic numbers as vectors.  Our triple is then itself a $3 \times 3$ matrix.  No matter which direction you pick, this type of estimate pushes the limits our or integer storage as our approximations become very accurate.

\begin{thebibliography}{}

\item Artur Avila, Vincent Delecroix \textbf{Some monoids of Pisot matrices}  \texttt{arXiv:1506.03692}
\item Viggo Brun \textbf{Algorithmes Euclidiens Pour Trois et Quatre Nombres}, Congr. Math. Scand. XIII, (1957), 45–64 \texttt{http://jolivet.org/timo/docs/Brun\_{}algo.pdf}
 
\end{thebibliography} 

\newpage 

\noindent Galois Theory could be approach from different perspectives not in textbooks:
\begin{itemize}
\item symmetric functions
\item module theory
\item diophantine approximation
\item dynamical systems
\end{itemize}
Especially the last one, turning algebraic numbers into dynamical systems could offer a new perspective. \\ \\
The polynomial $x^3 - x - 1$ has Galois group $S_3$ and spits into linear factors in the field 
$$K = \mathbb{Q}[x,y]/(x^3 - x - 1,y^2 + 23)$$
My question had been, if the Galois group is $S_3$ what are the three objects that are permuted?   \begin{itemize}
\item perhaps I've got the splitting field wrong? perhaps I'm using the wrong definition?
\item can we approximate the roots in some way?
\item how to primes split in this number field?
\end{itemize}
In any case, I believe there are three objects being permuted with the cubic $x^3 - x - 1$ and maybe we can find them.  Do we recall any linear algebra over $\mathbb{Q}$?  Linear algebra works over any field, but we tent to prefer fields that are algebraically complete.
$$ K \simeq 
\mathbb{Q}\cdot 1 \oplus 
\mathbb{Q}\cdot x \oplus 
\mathbb{Q}\cdot x^2 \oplus 
\mathbb{Q}\cdot y \oplus 
\mathbb{Q}\cdot xy \oplus
\mathbb{Q}\cdot x^2 y   $$
As an abelian group $\mathbb{Q}$ is infinitely gerated -- the generators are all prime numbers -- yet we are claining \textbf{dimension = $1$}.  How shall we represent $x$ in this basis?
$$ x \mapsto
\left[ 
\begin{array}{l||ccc|ccc}
 & 1 & x & x^2 & y & xy & x^2 y \\ \hline\hline 
 1 &  0 & 1 & 0 & 0 & 0 & 0 \\
 x &  0 & 0 & 1 & 0 & 0 & 0 \\
 x^2 & 1 & 1 & 0 & 0 & 0 & 0 \\ \hline
 y & 0 & 0 & 0 & 0 & 1 & 0 \\
 xy & 0 & 0 & 0 & 0 & 0 & 1 \\
 x^2 y & 0 & 0 & 0 & 1 & 1 & 0 
\end{array}\right] $$
and there's similar matrix for $y$:
$$ y \mapsto
\left[ 
\begin{array}{l||ccc|ccc}
 & 1 & x & x^2 & y & xy & x^2 y \\ \hline \hline
 1 &  0 & 0 & 0 & 1 & 0 & 0 \\
 x &  0 & 0 & 0 & 0 & 1 & 0 \\
 x^2 & 0 & 0 & 0 & 0 & 0 & 1 \\ \hline
 y & -23 & 0 & 0 & 0 & 0 & 0 \\
 xy & 0 & -23 & 0 & 0 & 0 & 1 \\
 x^2 y & 0 & 0 & -23 & 0 & 0 & 0 
\end{array}\right] $$
and we have a representaion of $S_3$ in $6 \times 6$ matrices, once we find the appropriate images of $x$.  We also know that symmetric polynomials in 3 variables are all going to remain in $\mathbb{Q}$ or possibly even $\mathbb{Z}$, so we can always expect lots of cancellations to occur.  Is that knowledge ever an advantage?
\end{document}