\documentclass[12pt]{article}
%Gummi|065|=)
\usepackage{amsmath, amsfonts, amssymb}
\usepackage[margin=0.5in]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}

\newcommand{\off}[1]{}
\DeclareMathSizes{20}{30}{20}{18}

\newcommand{\two }{\sqrt[3]{2}}
\newcommand{\four}{\sqrt[3]{4}}
\newcommand{\red}{\begin{tikz}[scale=0.25]
\draw[fill=red, color=red] (0,0)--(1,0)--(1,1)--(0,1)--cycle;\end{tikz}}
\newcommand{\blue}{\begin{tikz}[scale=0.25]
\draw[fill=blue, color=blue] (0,0)--(1,0)--(1,1)--(0,1)--cycle;\end{tikz}}
\newcommand{\green}{\begin{tikz}[scale=0.25]
\draw[fill=green, color=green] (0,0)--(1,0)--(1,1)--(0,1)--cycle;\end{tikz}}

\newcommand{\sq}[3]{\draw[#3] (#1,#2)--(#1+1,#2)--(#1+1,#2+1)--(#1,#2+1)--cycle;}

\usepackage{tikz}

\newcommand{\susy}{{\bf Q}}
\newcommand{\RV}{{\text{R}_\text{V}}}

\title{Worksheet: Prime Number Theorem}
\author{John D Mangual}
\date{}
\begin{document}

\fontfamily{qag}\selectfont \fontsize{12.5}{15}\selectfont

\maketitle

\noindent Studying the Prime Number Theorem was meant just to be a template of a much broader class.  In my opinion, the arguments are not very visual, or ``elementary".  Many people are making the point that ``elementary" proofs are more complicated then the Complex Analysis proof. \\ \\
If I complain that way, and have received such a negative response, then I can argue in a visual elementary way, and the proof should new.  Since all PNT problems seem to be about the hardness, I could imagine two engines for a proof:
\begin{itemize}
\item Stirling's formula
\item Horocycle flow
\end{itemize}
So far I haven't been able to give a complete answer.  Every day I'm learning a bit. \\ \\
The argument's from the 1930's and 1940's all have a similar flavor.  Starting from Stirling's formula for $n!$.\\ \\
\textbf{\#1} The first step of Norbert Weiner's argument looks like M\"{o}bius inversion, but possibly the lattice point counting on a hyperbola:
$$ \sum_{m=0}^\infty (\log m) x^m = \sum_{n=1}^\infty \sum_{m=1}^\infty \Lambda(n) \, x^{-mn\, } =  \sum_{n= 0}^\infty \Lambda(n) \frac{x^n}{1 - x^n} $$
If I evaluate at $x = 1$, the left side looks like logarithm of factorial:
$$ \log \big(\infty  ! \,\big) = \sum_{m=0}^\infty \big( \log m \big) = \sum \Lambda(n) \, \frac{1}{0} $$
Writing it this way would have been offensive to everyone at the time. We spend the rest understand the behavior at $x \approx 1$. This is my \textbf{regularization} approach to PNT.  I don't think anyone else thinks of it quite this way.  \\ \\
I tried setting $x = 1 + \epsilon$.  This is has a few derived approximations:
$$ x^m = (1 + \epsilon)^m = 1 + m \epsilon + \dots \hspace{0.25in}\text{and}\hspace{0.25in} \frac{x^n}{1 - x^n} =\frac{(1+ \epsilon)^n}{1 - (1+ \epsilon)^n}
= \frac{1 + n \epsilon }{1 - (1 - n \epsilon)} = 1 + \frac{1}{n \epsilon} $$
and if some small things get away, we can look at with a microsope and get more terms.
$$ \sum_{m=0}^\infty (\log m) \big(1 + m \epsilon\big) = \sum_{n=1}^\infty \sum_{m=1}^\infty \Lambda(n) \, \big(1 + mn \epsilon \big)  =  \sum_{n= 0}^\infty \frac{\Lambda(n)}{n} \big( 1 + \frac{1}{n \epsilon}\big)$$
Algebra always does more than we tell it to.  While this algebra is not correct, we can read it and know a little bit

\newpage

\noindent I do not like the way the next few lines were written so, I can do it over. It's not obvious at all to me that:
$$ \sum_{m=1}^\infty \big(\log m \big) \frac{x^m - x^{m+1}}{1-x} \stackrel{??}{=} \frac{x}{1-x} \sum_{m=1}^\infty  \log \Big( 1 + \frac{1}{m}  \Big) \, x^m $$
Norbert Weiner is suggesting there is an equality here.  There is also someting about M\"{o}bius transformations:
$$ x \mapsto x + 1 \hspace{0.25in}\text{and}\hspace{0.25in} x \mapsto \frac{x}{1-x}
\hspace{0.25in}\text{or}\hspace{0.25in}m \mapsto 1+\frac{1}{m}$$
Issues like this are not commented on in the paper.  He had other things in mind.
$$ \log \left( 1 + \frac{1}{m} \right)  - \frac{1}{m} = O \left(\frac{1}{m^2} \right) $$
He needed to keep track of exactly how bad the approximation $\log(1 + m^{-1})\approx \frac{1}{m}$ could be:
$$ \frac{x}{1-x}\sum_{m=1}^\infty \left[ \frac{1}{m} + O\left( \frac{1}{m^2}\right) \right] x^m  = 
\frac{x}{1-x}\sum_{m=1}^\infty \left[ \frac{1}{m} \right] x^m 
+ 
\underbrace{\frac{x}{1-x} \sum_{m=1}^\infty \left[ O\left( \frac{1}{m^2}\right) \right] x^m }_{??} $$
We don't know how large the derivative could be... but before we do that, what have we been estimating? \\ \\
\textbf{\#1 : crazy regularized factorial} 
$$ (\infty!)(x) := \sum_{m=0}^\infty (\log m) x^m \;\approx\; \frac{x}{1-x}\sum_{m=1}^\infty \left[ \frac{1}{m} + O\left( \frac{1}{m^2}\right) \right] x^m  $$
\textbf{\#2 : ( derivative of ) crazy regularized factorial}
\begin{eqnarray*}  \xi \frac{d}{d\xi} \Big[ \xi \,(\infty!)(e^{-\xi}) \Big] 
&=& \frac{\xi e^{-\xi} (1 - \xi - e^{-\xi} )}{(1 - e^{-\xi})^2} \left[ \log(1 - e^{-\xi}) -  \sum_{m=1}^\infty  O\left( \frac{1}{m^2} e^{-m \xi} \right) \right]  \\ \\ \\
&+& \frac{\xi^2 e^{-\xi}}{1 - e^{-\xi}} \left[ \frac{e^{-\xi}}{1 - e^{-\xi}} + \sum_{m=1}^\infty
O\left( \frac{1}{m} \right) e^{-m\xi}\right]   \end{eqnarray*}
What does that mean\dots to take a derivative of a random series? Even if it's small? \\ \\
In the end\dots since I don't really know what he's saying and nobody's really there to explain to me, no not much progress. \\ \\
Everyone is busy.  I understand.  It can wait. \\ \\
Norbert Weiner was the grandfather of random process theory -- the same collection of ideas we can use to study the weather or the stock market.  What's it doing here in Prime Number Theory, which I thought would be pretty regular? \\ \\
Doesn't this look like the partition function from statistical thermodynamics?  I'm getting really skeptical.   \\ \\Yet we proceed\dots

\newpage

\noindent We've basically shown that:
$$ \lim_{\xi \to 0} \xi \sum_{n=1}^\infty  \Lambda(n) \, \frac{d}{d(n\xi)} \left( \frac{ n \xi \, e^{-n\xi}}{e^{-n\xi}-1} \right) = 1$$
or if we want to be ``precise"
$$ \xi \sum_{n=1}^\infty \Lambda(n) \,  \frac{d}{d(n\xi)} \left( \frac{ n \xi \, e^{-n\xi}}{e^{-n\xi}-1} \right) = 1 + O(\xi \log \xi) $$
This is the M\"{o}bius inversion of the formulas on the previous page.
$$N_1(x) = ``g(x)"  = \frac{d}{dx} \left( \frac{  x }{ 1 - e^x} \right)
= \left\{ \begin{array}{ll}
O(1) & x \to 0 \\
O(xe^{-x}) & x \to \infty
 \end{array} \right.$$
This ``kernel" function is behaving one way for small umbers $x \ll 1$ and one way for large number $x \gg 1$.  This is not the magical part anyway. \\ \\
Somehow:
$$ \Bigg[ \xi \sum_{n=1}^\infty \Lambda(n) \,  \frac{d}{d(n\xi)} \left( \frac{ n \xi \, e^{-n\xi}}{e^{-n\xi}-1} \right) = 1 + O(\xi \log \xi) \Bigg]
\to \Bigg[ \xi \sum_{n=1}^{1/\xi} \Lambda(n)  = 1 + O_?(\xi) \Bigg] $$
Turning the limit on the left into the limit on the right is where the bulk of the work remains.   \\ \\
Whether we're done really depends on who you are:
\begin{itemize}
\item number theorists are very comfortable manupulating sum without a ``picture" of what's going on; that this discussion is ``done"
\item a physicist would be satisfied stopping here without any Tauberian theorem.  And ``intepretaion" of this discussion could be nice? 
\item Quantum Field Theory routinely uses divergent series of a kind that GH Hardy would have disapproved, even though he wrote an excellent book called \textbf{Divergent Series}.
\item information theory? Did not exist until Claude Shannon in 1950.
\item geometry?  The mixing of the horocycle flow wouldn't be studied until the 1970's or 1990's ?
\end{itemize}
We're in the early 21st century and a lot as changed.  And it's a little bit dangerous for me to get stuck on one problem.

\begin{thebibliography}{}

\item GH Hardy \textbf{Divergent Series}  Oxford University Press, 1949/1973.

\end{thebibliography}

\newpage

\noindent 

\end{document}